Recognizing emotions with technology and starting discussions

### 2018-01-21 paper.tex
Add figures for results

\section{Results}
As described in \ref{method}, we have conducted prototype testing sessions with 13 participants. For each of these
participants, we have two pieces of data:
\begin{itemize}
    \item{Predicted emotions during the shown video, created by the prototype}
    \item{Results from the interview we had with each participant during the testing}
\end{itemize}
Furthermore, for every of the three available videos, we have expectations regarding the emotions at certain
times of the video. Using these pieces of data, we are interested in the following information from analyzing
the results:
\begin{itemize}
    \item{Do the participants agree with the emotions predicted by the prototype?}
    \item{Do the predicted emotions coincide with the expectations we had from certain videos?}
\end{itemize}

>>>>

\section{Results}
As described in \ref{method}, we have conducted prototype testing sessions with 13 participants. For each of these
participants, we have two pieces of data:
\begin{itemize}
    \item{Predicted emotions during the shown video, created by the prototype}
    \item{Results from the interview we had with each participant during the testing}
\end{itemize}
Furthermore, for every of the three available videos, we have expectations regarding the emotions at certain
times of the video. Using these pieces of data, we are interested in the following information from analyzing
the results:
\begin{enumerate}
    \item{Do the participants agree with the emotions predicted by the prototype?}
    \item{Do the predicted emotions coincide with the expectations we had for certain videos?}
\end{enumerate}
The first questions can be answered by cross-checking the data that the prototype generated, against the
answers from the participants during the interview. The second question can be verified by checking the
expected emotions at certain times in a video, against the average of all the participants who watched that
video. This will make it clear whether the expected emotion is also the dominant emotion at that time.
Finally, we can combine questions 1 and 2. If both results are positive; that is, the predicted emotions by the
prototype match up with our expectations, and are valid according to the participant, then we can conclude
that it's highly likely to be accurate.

\subsection{Test results}
We present a table with the results of the interview. The table gives an overview of the answers given by the
participants regarding the accuracy of the prototype. Furthermore, several line charts are given which show
the average emotions of all participants from each video, and the expected emotions as a dashed vertical line.

The analyzing of the data generated by the prototype was done using some custom code. This analyzer tool was
created using Python and the matplotlib\footnote{\url{https://matplotlib.org}}} library to generate the charts.
The analysis tool is available as well: \url{https://github.com/drtheuns/minor_riet_analysis}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth, scale=1]{chart_failarmy_small.png}
    \caption{Average emotions of participants with video "Failarmy"}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth, scale=1]{chart_neck_small.png}
    \caption{Average emotions of participants with video "Neck"}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth, scale=1]{chart_roast_small.png}
    \caption{Average emotions of participants with video "Roast"}
\end{figure}
